### 2021-04-23 paper/ase21/intro.tex
Revised two parts

$\tool$ takes mechanized JavaScript specifications from $\jiset$ and performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript.  ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors.
\inred{We define their type hierarchies based on subtype relations and fields for record and AST types.}
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all 864 versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

>>>>

$\tool$ takes mechanized JavaScript specifications from $\jiset$ and performs
a type analysis of compiled functions using \textit{specification types}
defined in ECMAScript.  ECMAScript contains not only JavaScript
language types but also specification types such as abstract syntax
trees (ASTs), internal list-like structures, and internal records
including environments, completions, and property descriptors.
We define their type hierarchies based on subtype relations.
For records and AST types, we also define their fields.
Using such type information, $\tool$ performs a type analysis and detects specification bugs using
a \textit{bug detector} consisting of four checkers: 1) a reference
checker, 2) an arity checker, 3) an assertion checker, and 4) an operand checker.
$\tool$ also uses a \textit{condition-based refinement} for type
analysis, which prunes out infeasible parts in abstract states by using conditions
of assertions and branches to improve the precision of type analysis.
We evaluated $\tool$ with all 864 versions in the official
ECMAScript repository for the recent three years from 2018 to 2021.
The experiments showed that the refinement technique could reduce the number of
false-positive bugs caused by spurious types inferred by imprecise type analysis.

### 2021-04-23 paper/ase21/overview.tex
Revised two parts

\paragraph{Reference Checker} The example JavaScript program first defines a
variable \jscode{f} without initialization, which has the value \jscode{undefined}.
It then assigns an anonymous function to \jscode{f} using the operator \jscode{??=}.
While the corresponding \textbf{Evaluation} algorithm in Figure~\ref{fig:example}(a) originally
used the \textbf{GetReferencedName} algorithm to get a reference name on line 4.a,
a contributor removed the \textbf{GetReferencedName} algorithm and replaced all its
invocations with accesses of the field [[ReferencedName]] on October 28, 2020.
However, the contributor missed several cases including the semantics of
\jscode{??=}, which was fixed by another contributor on November 3, 2020.
Thus, the unknown variable bug for \textbf{GetReferencedName} existed for 7 days,
which the reference checker can detect.

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, \textbf{IteratorBindingInitialization}
in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which existed for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
another bug existed in \textbf{IteratorBindingInitialization} of
\textit{FormalParameter} in Figure~\ref{fig:example}(c).
The additional \textit{environment} parameter may
contain \jscode{undefined} or an environment record exactly the same as
\textit{originalEnv} as described in the assertion on line 5.
\inred{However, the assertion missed that the initial commit
of the open development process on September 22, 2015 introduced
\jscode{undefined}, which led to the assertion failure bug last for 1,297 days until April 10, 2019.}
The assertion checker can detect such assertion failures.

>>>>

\paragraph{Reference Checker} The example JavaScript program first defines a
variable \jscode{f} without initialization, which has the value \jscode{undefined}.
It then assigns an anonymous function to \jscode{f} using the operator \jscode{??=}.
While the corresponding \textbf{Evaluation} algorithm in Figure~\ref{fig:example}(a) originally
used the \textbf{GetReferencedName} algorithm to get a reference name on line 4.a,
a contributor removed the \textbf{GetReferencedName} algorithm and replaced all its
invocations with accesses of the field [[ReferencedName]] on October 28, 2020.
However, the contributor missed several cases including the semantics of
\jscode{??=}, which was fixed by another contributor on November 3, 2020.
Thus, the unknown variable bug for \textbf{GetReferencedName} lasted for 7 days,
which the reference checker can detect.

\paragraph{Arity Checker} The program finally calls \jscode{f} with an argument \jscode{true}.
During the initialization of the function call, \textbf{IteratorBindingInitialization}
in Figure~\ref{fig:example}(b) is executed with additional parameters \textit{iteratorRecord} and
\textit{environment} to assign argument values to parameters.
However, a contributor missed passing additional arguments to them on line 2 in
\textbf{IteratorBindingInitialization} of \textit{ArrowParameters} on September 6, 2018.
It caused an arity mismatch bug, which lasted for 533 days until another
contributor fixed it on February 20, 2020. The arity checker can detect such arity mismatches.

\paragraph{Assertion Checker} During the initialization of the function call,
\textbf{IteratorBindingInitialization} of \textit{FormalParameter} in Figure~\ref{fig:example}(c)
contains another bug.
Even though the additional \textit{environment} parameter may contain \jscode{undefined},
a contributor did not consider it on line 5 in the initial commit of the open development process
on September 22, 2015.  It caused an assertion failure bug, which lasted for 1,297 days until another
contributor fixed it on April 10, 2019.
The assertion checker can detect such assertion failures.
